Fully Automatic Loop-free Program Synthesis by Bounded Model Checking

### 2013-10-04 paper/paper.tex
Change title & authors
Bibtex

%\usepackage{makeidx}  % allows for indexgeneration
%
\title{{\sc Kalashnikov}: Fully Automatic Loop Free Program Synthesis by Bounded Model Checking}
\author{Matt Lewis}
\institute{Oxford University}

@@

Program synthesis is the mechanized construction of software that provably
satisfies a given specification.  Synthesis tools promise to relieve the
programmer from thinking about \emph{how} the problem is to be solved;
instead, the programmer only provides a compact description of \emph{what}
is to be achieved.  Foundational research in this area has been
exceptionally fruitful, beginning with Alonso Church's work on the
\emph{Circuit Synthesis Problem} in the sixties.  In this paper, we present
a new method that brings the promise of automating programming closer to
application.

\section{Related Work}
The most similar work to ours is {\sc brahma}~\cite{brahma}, which is also a method for
synthesizing loop-free bitvector programs.  In~\cite{brahma} the authors characterise
the program synthesis problem as a second order $\exists \forall$ formula, and
described the CEGIS algorithm for solving these formulae.  This algorithm reduces
the satisfiability of the $\exists \forall$ formula to the satisfiability of several
first order formulae, each of which can be decided using an off-the-shelf SMT solver.
{\sc Brahma} takes as input a specifcation (an SMT formula) and a library of components
(one component is more or less a single machine instruction).  It then finds
a permutation of the component library which satisfies the specification.  This
permutation is the final synthesised program.  In the event that the library does
not contain enough components to synthesise a correct program, the user is told
that the library is too small and is required to add more components until
the synthesis succeeds.  Each round of synthesis amounts to solving an
$\exists \forall$ formula that is quadratic in the size of the component library.

@@

\subsection{Why use C- instead of SAT?}
To misquote David Wheeler: ``all problems in computer science can be solved by
another level of abstraction.''~\cite{wheeler-abstraction}.  C- serves as
an abstraction of SAT.  We can think of SAT as an assembly language and
{\sc cbmc} as a compiler for C- to this assembly language.  The benefits
of using C- as our logic rather than SAT are very similar to the benefits of
writing code in a high level language rather than assembly language.
Some of the more significant advantages are:

@@

>>>>

%\usepackage{makeidx}  % allows for indexgeneration
%
\title{Fully Automatic Loop-free Program Synthesis by Bounded Model Checking}
\author{Daniel Kroening \and Matt Lewis}
\institute{Oxford University}

@@

Program synthesis is the mechanized construction of software that provably
satisfies a given specification.  Synthesis tools promise to relieve the
programmer from thinking about \emph{how} the problem is to be solved;
instead, the programmer only provides a compact description of \emph{what}
is to be achieved.  Foundational research in this area has been
exceptionally fruitful, beginning with Alonzo Church's work on the
\emph{Circuit Synthesis Problem} in the sixties~\cite{church-synth}.
In this paper, we present a new method that brings the promise of
automating programming closer to application.

\section{Related Work}
The closest work to ours is {\sc brahma}~\cite{brahma}, which is also a method for
synthesizing loop-free bitvector programs.  In~\cite{brahma} the authors characterise
the program synthesis problem as a second order $\exists \forall$ formula, and
described the CEGIS algorithm for solving these formulae.  This algorithm reduces
the satisfiability of the $\exists \forall$ formula to the satisfiability of several
first order formulae, each of which can be decided using an off-the-shelf SMT solver.
{\sc Brahma} takes as input a specifcation (an SMT formula) and a library of components
(one component is more or less a single machine instruction).  It then finds
a permutation of the component library which satisfies the specification.  This
permutation is the final synthesised program.  In the event that the library does
not contain enough components to synthesise a correct program, the user is told
that the library is too small and is required to add more components until
the synthesis succeeds.  Each round of synthesis amounts to solving an
$\exists \forall$ formula that is quadratic in the size of the component library.

@@

\subsection{Why use C- instead of SAT?}
To misquote David Wheeler: ``all problems in computer science can be solved by
another level of abstraction.''~\cite{beautiful-code}.  C- serves as
an abstraction of SAT.  We can think of SAT as an assembly language and
{\sc cbmc} as a compiler for C- to this assembly language.  The benefits
of using C- as our logic rather than SAT are very similar to the benefits of
writing code in a high level language rather than assembly language.
Some of the more significant advantages are:

@@

\bibliography{synth}{}
\bibliographystyle{splncs}
